Article title

### 2017-07-13 paper-webserver.tex
CHANGE: sentance

Spfy enables processing of thousands of genome sequences using multiple modules. By using task queue workers, enabled by the Python-based Redis Queue library \url{https://github.com/nvie/rq}, performance can quickly scale to available infrastructure. As a bioinformatics tool, we ensured reliability of the platform by integrating the open-source Sentry toolkit \url{https://github.com/getsentry/sentry} for real-time exception tracking. Containers are orchestrated through Docker-Compose allowing the entire platform: webservers, databases, and task workers, to be easily replicated by other researchers. We present Spfy as a template for brining advances in web application development and deployment to online bioinformatics platforms.

We designed Spfy's front-end following the Material Design standards \url{https://material.io/}, released by Google. The user interface is implemented with the React JavaScript library \url{https://facebook.github.io/react/}, as a single-page application to allow efficient data-flow without reloading the website. Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.

>>>>

We designed Spfy's front-end following the Material Design standards \url{https://material.io/}, released by Google.
The user interface is implemented with the React JavaScript library \url{https://facebook.github.io/react/}, by Facebook, as a single-page application to allow efficient data-flow without reloading the website.
Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.

Spfy enables processing of thousands of genome sequences using multiple modules.
By using task queue workers, enabled by the Python-based Redis Queue library \url{https://github.com/nvie/rq}, performance can quickly scale to available infrastructure.
As a bioinformatics tool, we ensured reliability of the platform by integrating the open-source Sentry toolkit \url{https://github.com/getsentry/sentry} for real-time exception tracking.
Containers are orchestrated through Docker-Compose allowing the entire platform: webservers, databases, and task workers, to be easily replicated by other researchers.
We present Spfy as an integrated predictive genomics toolkit for pathogens / \textit{E. coli} which leverages advances in web application development and deployment.
